### 2016-07-26 sections/R10.01.tex
# Conflicts: #	sections/image_texts/all.tex

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{One dimensional self-organizing maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of data. 
    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible.
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.
%    In the following section, we are going to show how we used 1D SOMs to extract information from available data in M31.
%Clustering
 %   \subsection{Clustering M31 data}

@@

        %%%Talking about four right regions
        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH line fluxes compared to other regions (Fig. 5 in \cite{Dim15}). 
        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
        The higher values for these quantities could be the reason that these 4 regions become separated from the others in the $1\times2$ network.
        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions might be the reason for regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
        Similarities with the other regions in the other input values causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
       % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.

@@

        \begin{figure}
            \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
             }
            \hfill
            \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
            \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
             }
             \hfill
            \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
             }%%% What should I do with this one! It doesn't look good visually
            \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids. The axes show the position of the neurons. The purple hexagonal shapes represent the neurons. The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum. The numbers in the plot show the M31 regions located in each neuron.}
            \label{fig: M31_nets_1d}
        \end{figure}

@@

    \subsection{Inside the 2 neuron network}%%% I will find better title for this subsection
        %What is going on in this section
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups were separated from each other for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure}
        \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure}

@@

       Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meaning, we have to mention that we only used 6 regions to calculate these correlation coefficients.
       The number of data points is not high enough to yield a strong conclusion about PAH properties in M31.%%% it doesn't sound right:((
        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differ from the correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), the SOM separated a hidden cluster of the data which has different properties. %%Again eh!

>>>>

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 1: 1D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{One dimensional self-organizing maps}
    \label{Sec: 1d_cluster}
%Why 1D maps are useful
    The purpose of  exploring the M31 data with 1D maps is to monitor the general behaviour of the data. 
    One-dimensional SOMs can have the minimum number of clusters, $1\times2$, up to the highest number of clusters possible.
    In a small sample like ours, smaller grid SOMs are very useful to find correlations that cannot be found without  clustering the data.
    On the other hand, larger grid 1D SOMs are a helpful tool to get quick insight into the data.

    \subsection{Clustering M31 data}%I am not sure about it

@@

        %%%Talking about four right regions
        \cite{Dim15} showed that regions 1, 2, 9, and 10 have higher PAH line fluxes compared to other regions (Fig. 5 in \citealt{Dim15}). 
        %Regions 1, 2, and 9 are in the 10~Kpc ring and region 10 is located in the bulge of M31; however, regions 3 to 8 are located slightly out of the inner ring or the 10~kpc one.
        These regions also have relatively high intensities in all the mid-infrared and far-infrared bands and have high dust luminosity and dust mass.
        The higher values for these quantities could be the reason that these 4 regions become separated from the others in the $1\times2$ network.
        Regions 1 and 9 are in the 10~kpc ring, region 2 is slightly out of the 10~kpc ring and region 10 is in the bulge of M31; however, regions 3 to 8 are located out of the inner ring or the 10~kpc ring (Fig.~\ref{fig: regions in m31}).   
        The differences in their positions might be the reason for regions 1, 2, 9 and 10 having higher values in some quantities than the others. 
        Similarities with the other regions in the other input values causes regions 1, 2, and 9 to gradually move towards other regions and away from region 10 in the higher grid SOMs.
       % Therefore, in 1D networks with 14 neurons or higher, regions 1, 2, and 9 completely are separated from region 10, and show more similarity to other regions than to the region 10.

@@

    \begin{figure}
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
        \caption{$1\times2$~network}
    \label{fig: M31_net_1by2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
         \caption{$1\times3$~network}
        \label{fig: M31_net_1by3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
        \caption{$1\times14$~network}
        \label{fig: M31_net_1by14}
    \end{subfigure}
   \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids. The axes show the position of the neurons. The purple hexagonal shapes represent the neurons. The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum. The numbers in the plot show the M31 regions located in each neuron.}
   \label{fig: M31_nets_1d}
    \end{figure}

% \end{figure}
%         \begin{figure}
%             \subfloat[$1\times2$~network\label{fig: M31_net_1by2}]{
%              \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by2_all.png}
%              }
%             \hfill
%             \subfloat[$1\times3$~network\label{fig: M31_net_1by3}]{
%             \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by3_all.png}
%              }
%              \hfill
%             \subfloat[$1\times14$~network\label{fig: M31_net_1by14}]{
%              \includegraphics[width=0.5\textwidth]{../images0.01/M31/1D/combine_1D_1by14_all.png}
%              }
%              %%% What should I do with this one! It doesn't look good visually
%             \caption{SOM of the M31 data from $1\times2$, $1\times3$~and $1\times14$~grids. The axes show the position of the neurons. The purple hexagonal shapes represent the neurons. The grey scale colours show the differences between weight of the neurons, with white as the minimum difference and black as the maximum. The numbers in the plot show the M31 regions located in each neuron.}
%             \label{fig: M31_nets_1d}
%         \end{figure}

@@

    \subsection{Inside the 2 neuron network}

        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups were separated from each other for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure*}
        \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}
        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure*}

@@

       Regardless of the fact that some of the (anti)-correlations in Fig.~\ref{fig: cor_cluster1} might have physical meaning, we have to mention that we only used 6 regions to calculate these correlation coefficients.
       The number of data points is not high enough to yield a strong conclusion about PAH properties in M31.
        However, we can conclude that since the correlation coefficients derived from the clustered data (Fig.~\ref{fig: cor_cluster1}) differ from the correlation coefficients derived from the data from the all regions (Fig.~\ref{fig: cor_all}), the SOM separated a hidden cluster of the data which has different properties.

### 2016-07-26 sections/R20.01.tex
# Conflicts: #	sections/image_texts/all.tex

 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 2: 2D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
 \section{Two dimensional self-organizing maps}
 \label{sec: 2d_cluster}
    Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
    In 2D networks, each neuron has two to six neighbours, which allows them to to capture a complete picture of the complicated relations in the input data.
    Accordingly, we created $10\times10$ 2D networks to study the data in detail.
    As mentioned in previous sections, the size of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.
    In this section we chose $10\times10$ size despite knowing, from the size of our input data, that most of the neurons would be empty.
    Using 2D networks, we are mostly interested in the ability of the SOMs to show the underlying structure of the data rather than its clustering features.
    \import{../sections/image_texts/}{all.tex}
    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of the M31 data.
    Similar to Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.

@@

            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data) gradually, by adding other quantities to the input data. 
            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e. the SOM in Fig~\ref{fig: inc_D_col3s}a was created from PAH and H$\alpha$ emission as input data, the SOM in Fig~\ref{fig: inc_D_col3s}b created from PAHs, H$\alpha$ emission and [\sii] continuum, and so on. 
            \import{../sections/image_texts/}{col3byall.tex}

            The SOM algorithm assigns a random weight to each network that causes the overall position of regions in networks (even with the same input data) to change in each run of the algorithm.
            However, the position of each region relative to other regions changes dramatically only when the new sets of input data are given to the algorithm (assuming all the initial values for the run are unchanged).
            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: inc_D_col3s}a,~\ref{fig: inc_D_col3s}d,~\ref{fig: inc_D_col3s}g,~\ref{fig: inc_D_col3s}k, and ~\ref{fig: inc_D_col3s}l, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
            In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data.

            Comparing Figs.~\ref{fig: inc_D_col3s}a to ~\ref{fig: inc_D_col3s}o shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
            Increasing the dimension of the input data makes region 10 more isolated.
            The relative positions of regions 4 and 7 stay the same with increasing the dimensions of the input data. 
            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revoke those changes.

>>>>

 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Result Part 2: 2D SOMs
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
 \section{Two dimensional self-organizing maps}
 \label{sec: 2d_cluster}
    Although 1D networks are helpful to give a general idea about the data, neurons in 1D maps have a maximum of two neighbours, which can limit the usefulness of the results.
    In 2D networks, each neuron has two to six neighbours, which allows them to to capture a complete picture of the complicated relations in the input data.
    Accordingly, we created $10\times10$ 2D networks to study the data in detail.
    As mentioned in previous sections, the size of SOMs are arbitrary and must be decided by users based on their goals for use of the SOM.

    In this section we chose $10\times10$ size despite knowing, from the size of our input data, that most of the neurons would be empty.
    Using 2D networks, we are mostly interested in the ability of the SOMs to show the underlying structure of the data rather than its clustering features.
    Fig.~\ref{fig: all_derived_ones} shows the 2D SOM of the M31 data.
    Similar to Fig.~\ref{fig: M31_net_1by14}, all the 10 regions are completely separated from each other in Fig.~\ref{fig: all_derived_ones}.
    \import{../sections/image_texts/}{all.tex}

@@

            We increased the dimension of input data in Fig.~\ref{fig: only_pahs} (PAH only data) gradually, by adding other quantities to the input data. 
            The order in which data were added is the same as the order in Fig.~\ref{fig: cor_all}, i.e. the SOM in Fig~\ref{fig: col3and11_dist} was created from PAH and H$\alpha$ emission as input data, the SOM in Fig~\ref{fig: col3and12_dist} created from PAHs, H$\alpha$ emission and \sii~ continuum, and so on. 
            \import{../sections/image_texts/}{col3byall.tex}

            The SOM algorithm assigns a random weight to each network that causes the overall position of regions in networks (even with the same input data) to change in each run of the algorithm.
            However, the position of each region relative to other regions changes dramatically only when the new sets of input data are given to the algorithm (assuming all the initial values for the run are unchanged).
            In all SOMs in Fig~\ref{fig: inc_D_col3s}, region 10 is located in the corner of the SOMs, but in  Figs~\ref{fig: col3and11_dist},~\ref{fig: col3and14_dist},~\ref{fig: col3and17_dist},~\ref{fig: col3and21_dist}, and ~\ref{fig: col3and22_dist}, it is placed in the left side of the SOMs and in the others it is in the right side of the networks.
            In our discussion on differences between networks, we do not address the changes in the network due to initialization of the SOM algorithm and only consider the effect of changing the input data.

            Comparing Figs.~\ref{fig: col3and11_dist} to ~\ref{fig: col3and25_dist} shows that adding \halpha~emission data to PAH features causes regions 9 and 10 become isolated. 
            Increasing the dimension of the input data makes region 10 more isolated.
            The relative positions of regions 4 and 7 stay the same with increasing the dimensions of the input data. 
            Adding SPIRE 350, 500~$\mu$m emission and L$_{\rm dust}$ does not have any obvious effect on the networks.
            Stellar mass, total gas mass, dust mass and RHI data alternate the distances between neurons effectively, but it seems that adding SFR, L$_{\rm TIR}$ and metallicity data revoke those changes.

### 2016-07-26 sections/V0.0/R10.0.tex
# Conflicts: #	sections/image_texts/all.tex

    \subsection{Inside the 2 neuron network}%%% I will find better title for this subsection
        %What is going on in this section
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups were separated from each other for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure}
        \includegraphics[width=0.5\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure}

@@

        The anti-correlation between stellar mass and PAHs could be result of the position of the regions in M31.
        Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an H {\sc II} region, which could be the reason of low PAHs for these regions.
        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
        %% Sahar: Can we have higher PAHs absorbes stellar mass and thats why we see the anti-correlation?!!!

>>>>

    \subsection{Inside the 2 neuron network}
        %What is going on in this section
        \label{sec: inside_the_2_neurons}
        Using self-organizing maps, we can identify hidden subgroups in our samples. 
        Each of these subgroups were separated from each other for a reason.
        This reason can vary from having higher values in some specific properties, as discussed in Sec.~\ref{Sec: 1d_cluster}, to some unknown correlations between data that cannot be seen in other groups or in the galaxy as a whole.
        To investigate the latter, we show in Fig.~\ref{fig: cor_cluster1} the Pearson correlation coefficients for the inputs from regions 3 to 8, which were clustered together in the $1\times2$ and $1\times3$ networks (see Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}).

        \begin{figure*}
        \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_derived_3_to_8_core_plot_for_paper.pdf}%%% cut the white regions around the figure
        \caption{Same as Fig.~\ref{fig: cor_all}, but here we used data from regions grouped in the left sides of Figs.~\ref{fig: M31_net_1by2} and ~\ref{fig: M31_net_1by3}. }
          \label{fig: cor_cluster1}
        \end{figure*}

@@

        The anti-correlation between stellar mass and PAHs could be result of the position of the regions in M31.
        Regions 5, 6, and 8 are located on the stellar disk of the galaxy and have relatively high stellar mass and low PAHs. 
        According to~\cite{Dim15}, regions 5 and 8 are the only two regions in our sample that do not include an H {\sc II} region, which could be the reason of low PAHs for these regions.
        Regions 4 and 7 have similar quantities for both stellar mass and PAHs and region 3 has high PAHs and low stellar mass.
        Without data from more regions in M31, we cannot confidently say that higher stellar mass decreases PAH fluxes.
        %% Sahar: Can we have higher PAHs absorbs stellar mass and that's why we see the anti-correlation?!!!

### 2016-07-26 sections/data0.01.tex
# Conflicts: #	sections/image_texts/all.tex

Our study includes 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}). 
These specific regions were chosen for the availability of mid-infrared PAH spectroscopy.
Besides PAH line strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
Table~\ref{tab: data} shows the full list of data and their units for both M31 and M101.
Observed values were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
Since the spatial resolution of the observations varies from $<1$\arcsec to 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g. the spectroscopic data).
In this project we used flux per unit area, which the convolution methods conserve~\citep{Aniano12}, as the input data.
Therefore, we did not perform any resolution matching and used data at their original resolution. %PB: Need to discuss these last few sentences; not sure I understand what you're saying.

@@

% \begin{figure}
%   \begin{subfigure}[b]{0.5\textwidth}
%         \centering
%     %\centering
%         \includegraphics[width=0.97\textwidth]{../images0.0/M31/M31.png}
%         \caption{MIPS24 image of M31, with position of 10 regions that we studies.}
%         \label{fig: regions in m31}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[b]{0.5\textwidth}
%         \includegraphics[width=\textwidth]{../images0.01/M101/M101.png}
%         \caption{IRAC1 image of M101, with position of our 8 regions that we studies.}
%     \label{fig: regions in m101}
%     \end{subfigure}
%     \caption{Position of the data in M31 (up) and M101 (down).}
% \end{figure}

  \begin{figure}
    \subfloat[MIPS 24~$\mu$m image of M31~\citep{Gordon06}, with position of 10 regions from~\cite{Dim15} \label{fig: regions in m31}]{
      \includegraphics[width=0.5\textwidth]{../images0.01/M31/M31.png}
    }
    \hfill
    \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
      \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
    \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
    \label{fig:dummy}
  \end{figure}

@@

     \cite{Dim15} using {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31. 
     Fluxes and equivalent widths of PAH and atomic line features were measured using the~{\sc PAHFIT IDL} tool~\citep{Smith07b}.
     \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
     We used the measured PAH feature fluxes, metallicity and RHI of each region as an input for SOMs.

    For the photometry part of the sample, we used the \GALEX~\citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha, \sii~and \oiii narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0$\mu$m images ~\citep{Barmby06}; MIPS24 and 70~$\mu$m~images\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
     The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (H\,{\sc I}) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m), stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) from \cite{Rahmani16}, and L$_{\rm dust}$ and mass from \cite{Draine14}.

    \subsection{M101 observations}
    \label{Sec: data_M101_SOMN} 
     \cite{Gordon08} measured PAH fluxes, metallicity and RHI for M101 in 8 regions chosen.. % PB: reason for selecting?
%     We also added their measurement of metallicity and RHI for these regions to our sample.
     We used NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather imaging observations of M101, including 
      \GALEX FUV and NUV~\citep{depaz07}, IRAC $3.6-8.0\mu$m, MIPS~24 and 70~$\mu$m~\citep{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
     As for M31, we used $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Helfer03} and atomic gas (H\,{\sc I}) 21~cm emission images from \cite{Walter08}.
     SFR(FUV + 24$\mu$m), stellar and total gas mass maps were calculated using the same methods as for M31.

     Some of the correlations between single-wavelength emission and galaxy properties are well-known.
     Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g]{Leitherer99,Smith07a} and it can be used to calculate the stellar mass~\citep{Eskew12}.
     FUV, \halpha, and TIR emission are indicators of star forming regions.
     In this project we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24$\mu$m emission.
     Total infrared emission is calculated from a modified version of~\cite{Draine07} calibration using using 8, 24, 70, and 160 $\mu$m emission~\citep{Boquien10}.
     To make sure that we do not use the observed data as input data in multiple forms, we removed all the observed data that were used to calculate galaxies properties from the input sample.
     We used this sample of observations as the main input for creating SOMs.
     Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients between the observations computed with a confidence level of $95\%$.

      \begin{figure*}
                \centering
                \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
            \caption{Pearson correlation coefficients with a confidence level of 95$\%$ for all data in subset 0. The colours show the Pearson correlation coefficients where 1 means highly correlated and $-1$ means highly anti-correlated quantities. The non-significant correlations were left empty.}
            \label{fig: cor_all}
        \end{figure*}

>>>>

Our study includes 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}). 
These specific regions were chosen for the availability of \Spitzer/IRS 5 - 15$\mu$m  spectroscopy covering PAHs emission.
Besides PAH bands strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
Table~\ref{tab: data} shows the full list of data for both M31 and M101.
Observed values were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
Since the spatial resolution of the observations varies from $<1$\arcsec to 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g. the spectroscopic data).
In this project we used flux per unit area, which the convolution methods conserve~\citep{Aniano12}, as the input data.
Therefore, we did not perform any resolution matching and used data at their original resolution. %PB: Need to discuss these last few sentences; not sure I understand what you're saying.

@@

\begin{figure}
  \begin{subfigure}[b]{0.5\textwidth}
        \centering
    %\centering
        \includegraphics[width=0.97\textwidth]{../images0.01/M31/M31.png}
        \caption{MIPS24 image of M31, with position of 10 regions that we studies.}
        \label{fig: regions in m31}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{../images0.01/M101/M101.png}
        \caption{IRAC1 image of M101, with position of our 8 regions that we studies.}
    \label{fig: regions in m101}
    \end{subfigure}
    \caption{Position of the data in M31 (up) and M101 (down).}
\end{figure}

%   \begin{figure}
%     \subfloat[MIPS 24~$\mu$m image of M31~\citep{Gordon06}, with position of 10 regions from~\cite{Dim15} \label{fig: regions in m31}]{
%       \includegraphics[width=0.5\textwidth]{../images0.01/M31/M31.png}
%     }
%     \hfill
%     \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
%       \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
%     \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
%     \label{fig:dummy}
%   \end{figure}

@@

     \cite{Dim15} used {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31. 
     Fluxes and equivalent widths of PAH and atomic line features were measured using the~\textsc{pahfit idl} tool~\citep{Smith07b}.
     \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
     We used the measured PAH feature fluxes, metallicity and RHI of each region as an input for SOMs.

    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha, \sii~and \oiii narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0$\mu$m images~\citep{Barmby06}; MIPS24 and 70~$\mu$m~images\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
     The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\mathrm TIR}$) from \cite{Rahmani16}, and L$_{\mathrm dust}$ and mass from \cite{Draine14}.

    \subsection{M101 observations}
    \label{Sec: data_M101_SOMN}

     \cite{Gordon08} measured PAH fluxes and RHI for M101 in 8 star forming \hii~regions.
     Metallicity of 6 out of 8 regions were measured by~\cite{Kennicutt03} and the other two by~\cite{Gordon08}.
     We used the NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather imaging observations of M101, including 
      \GALEX FUV and NUV~\citep{depaz07}, IRAC $3.6-8.0\mu$m, MIPS~24 and 70~$\mu$m~\citep{Dale09}, and PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
     As with M31, we used $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Helfer03} and atomic gas (\hi) 21~cm emission images from \cite{Walter08}.
     SFR(FUV + 24$\mu$m), stellar and total gas mass maps were calculated using the same methods as for M31.

       \subsection{Preparing data for data mining}

     Correlations between some of single-wavelength emission and galaxy properties are well-known.
     Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g]{Leitherer99,Smith07a} and it can be used to calculate the stellar mass~\citep{Eskew12}.
     FUV, \halpha, and TIR emission are indicators of star forming regions.
     In this project we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24$\mu$m emission.
     Total infrared emission is calculated from a modified version of~\cite{Draine07} calibration using using 8, 24, 70, and 160 $\mu$m emission~\citep{Boquien10}.

    %To guarantee that we do not use the observed data as an input for SOM in multiple forms, we removed all the observed data that were used to calculate galaxies properties from the input sample.
    We removed all the observed data that were used to calculate galaxies properties from the input sample, to guarantee that they have not been used in multiple forms
   % We used this new sample of observational and derived data as the main input for creating SOMs.
    To have a prior knowledge on the data set, %or to have an insight into the data set!
    we computed the Pearson correlation coefficients between input data.
    Fig.~\ref{fig: cor_all} shows the Pearson correlation coefficients with a confidence level of 95 per cent. 
    All the PAHs are correlate with one another very well.
    They also highly correlate with SPIRE bands and PACS emission, L$_{\mathrm dust}$, L$_{\mathrm TIR}$, SFR and metallicity.
    Fluxes from PAHs 7.7, 8.3, 12.7 and 17~$\mu$m show weak ant-correlation with RHI.
    In general, PAHs in our data set highly correlate with most of the other quantities.

      \begin{figure*}
                \centering
                \includegraphics[width=\textwidth]{../images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
            \caption{Pearson correlation coefficients with a confidence level of 95 per cent for all data in subset 0. The colours and circles' size show the Pearson correlation coefficients where large blue circles are 1 which means highly correlated and large red circles are$-1$ means highly anti-correlated quantities. The non-significant correlations were left empty.}
            \label{fig: cor_all}
        \end{figure*}
